Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
Remove "in Haskell"
That would need to be "for Haskell", but "for Haskell" is ambiguous.  An
option that would work is "Haskell's version of Doctest", so we would
need to use that, if we really need this.
Add comment

\begin{itemize}
\item
    We originally implemented Doctest in Haskell and
    extended Haddock's markup to support examples, back in 2010
\item
    Add support for QuickCheck properties to Doctest and
    extend Haddock markup to support properties
    (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

@@

\begin{quote}
    \emph{sol: Can we remove what follows??}\\
    \emph{kazu: I want to keep them for readability.}
\end{quote}

@@

>>>>

\begin{itemize}
\item
    We originally implemented Doctest and
    extended Haddock's markup to support examples, back in 2010
\item
    Add support for QuickCheck properties to Doctest and
    extend Haddock markup to support properties
    (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

@@

\begin{quote}
    \emph{sol: Can we remove what follows?}

    \emph{kazu: I want to keep them for readability.}

    \emph{sol: For me it really depends on how often we use something.
    If we only use it once or twice, I'd try make it clear from the
    context what is meant.}
\end{quote}

@@

    sol: @kazu, this was primarily meant for @mkl as reference.
